Attributions for Poverty in Post-Socialist Countries

### 2014-02-15 article2013.Rmd
JA vielä lisää spämmiä!

---
title: Attributions for Poverty in Post-Socialist Countries
author: [Markus Kainu & Mikko Niemelä]
date: February 14, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
---

@@

This site gathers together all the data analysis behind the actual paper. Data analysis is broken down in three parts and each part is presented in .html format for human eyes and in text source including the R-code required for reproducing the analysis. As both the micro data and macro data are available as open data, anyone can rerun these analysis.

@@

Wilson, George (1996) Toward a Revised Framework for Examining Beliefs about the Causes of Poverty. The Sociological Quarterl

>>>>

---
title: Attributions for Poverty in Post-Socialist Countries
author: [Markus Kainu & Mikko Niemelä]
date: February 15, 2014
abstract: Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
keywords: poverty
output:
  pdf_document:
    toc: true
    number_section: true
---

@@

@@

Wilson, George (1996) Toward a Revised Framework for Exa
